\sysfull

### 2017-11-06 paper/coalescing.tex
First changes to coalescing section

\sys can coalesce an arbitrary number of consecutive tasks. As more tasks
coalesce, their collective commit overhead amortizes better, potentially
improving performance. As more tasks coalesce, the amount of potentially {\em
wasted work} also increases. If power fails during a long sequence of coalesced
tasks the lack of an intervening commit requires execution to restart from the
{\em first} task in the sequence, failing to preserve the progress of any of
the tasks in the long sequence. \sys moderates the risk of coalescing and
capitalizes on its benefit by dynamically, \emph{adaptively} determining a
coalescing factor that combines many tasks without suffering an excess of
wasted work.

@@

\sys determines $C$ for a given operation based on the number of tasks
completed, $S$, during the current operational period. \sys begins execution in
a coalesced task with $C$ initialized to half of the number of tasks executed
during the previous operating period and $S$ initialized to $0$. The system
executes $C-1$ coalesced tasks followed by one committing task. After each
commit, \sys assigns $C$ to half of $S$.   If more tasks complete in an
operating period, \sys attempts to coalesce more tasks. If fewer tasks
complete, \sys attempts to coalesce fewer tasks. If no committing task
completes due to a power failure, \sys updates $C$ on reboot to half of $S$
(the number of tasks completed before the power failure) and continues.

>>>>

\textbf{Task Coalescing Problem:} \sys can coalesce an arbitrary number of consecutive tasks. As more tasks coalesce, their collective commit overhead amortizes better, potentially improving performance. As more tasks coalesce, the amount of potentially {\em wasted work} also increases. If power fails during a long sequence of coalesced tasks the lack of an intervening commit requires execution to restart from the {\em first} task in the sequence, failing to preserve the progress of any of the tasks in the long sequence. \sys moderates the risk of coalescing and capitalizes on its benefit by dynamically, \emph{adaptively} determining a coalescing factor that combines many tasks without suffering an excess of wasted work.

@@

\textbf{Task Coalescing Strategies:} There are infinite possible strategies for coalescing (infinite amount of $(C_U,C_D)$ pairs). We will consider the three fundamental ones:

\begin{enumerate}
	\item \textbf{$N$ up/$N$ down:} where task coalescing factor increases by $N$ at each successful virtual task execution and decreases by $N$, otherwise;
	\item \textbf{History-driven:} where coalescing will consider history of power failures into deciding on $(C_U,C_D)$ values on the fly;
	\item \textbf{Program profiling-driven:} where coalescing strategy takes into account \emph{expected size} of each task in the application to pick the best coalescing factor.
\end{enumerate}

\subsection{Operation of $N$ up/$N$ Down Coalescing:} \todo{To be written}{Przemek}

\subsection{Operation of History-driven Coalescing}: \sys determines $C$ for a given operation based on the number of tasks completed, $S$, during the current operational period. \sys begins execution in a coalesced task with $C$ initialized to half of the number of tasks executed during the previous operating period and $S$ initialized to $0$. The system executes $C-1$ coalesced tasks followed by one committing task. After each commit, \sys assigns $C$ to half of $S$. If more tasks complete in an operating period, \sys attempts to coalesce more tasks. If fewer tasks
complete, \sys attempts to coalesce fewer tasks. If no committing task
completes due to a power failure, \sys updates $C$ on reboot to half of $S$
(the number of tasks completed before the power failure) and continues.

\subsection{Operation of Program Profiling-driven Coalescing:} \todo{To be written}{Przemek}
